Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-22 methods_paper/fabl-paper.tex
working on edits that i stupidly lost.

Record linkage is the task of identifying duplicate records across multiple data sources, often in the absence of a unique identifier \citep{christen2012data}. Record linkage is an increasingly important task in ``data cleaning," that is used for inferential and predictive analyses in fields such as statistics, computer science, machine learning, political science, economics, precision medicine, official statistics, and others.

>>>>

Record linkage is the task of identifying duplicate records across multiple data sources, often in the absence of a unique identifier \citep{christen2012data}. Record linkage is an increasingly important task in ``data cleaning," that is used for inferential and predictive analyses in fields such as statistics, computer science, machine learning, political science, economics, precision medicine, official statistics, and others. In the literature, bipartite record linkage is commonly known as merging two databases that contain duplication across the two databases, but do not contain any duplications within each database.

task consists of merging two disparate datafiles containing information on two overlapping sets of entities.
